\quad
\textbf{ Navn på virksomhet og kontaktperson/veileder}

\quad{Navnet på bedriften som praksisen skal utføres i er \textit{Solwr}. Navnet på kontaktperson/veileder er \textit{Andrea Tenti}.}\\

\textbf{Angivelse av hvordan praksisen skal gjennomføres (tidsrom)}

\quad{Fra 12. September 2024, skal studenten, \textit{Vegard Arnesen Mytting}, utføre 120 timer arbeid hos bedriften.}\\

\textbf{En skisse av praksisens innhold, hvilke arbeidsoppgaver som skal utføres og resultater som skal oppnås}

\quad{Praksisen vil inneholde arbeid som:}
\begin{itemize}
    \item \gls{trace} is a reporting tool for SOLWR customers. It is used to gather information from the various components of \gls{trace} and display them to the user. 
    \item The ABC module is a tool to perform Activity-Based Costing analysis; an accounting technique that splits the cost of a company across their portfolio of products in a fair way. 
    \item This project is about converting a python web application to a java web application and adding it as a module to \gls{trace}. The students will write the backend in Java and build the frontend with Vue3. The data is collected from the different databases, using SQL queries. 
\end{itemize}\\

\textbf{Angivelse av læringsmål for praksisen}

\quad{Læringsmålene fra praksisen vil være:}
\begin{itemize}
    \item Good software development practices. 
    \item Ability to perform research to best implement features. 
    \item Improve knowledge of languages, such as Java, sql, python, vue. 
    \item Acquire domain-specific knowledge in the field of logistics. 
\end{itemize}\\

\textbf{Faglig veileder og kontaktperson i bedrift}

\quad {Navnet på faglig veileder er \textit{Kjell Inge Tomren}. Kontaktpersonen i bedriften er \textit{Andrea Tenti}.}\\

\textbf{Tidsfrist for levering av praksisrapport}

\quad{13. Desember 2024, klokken 12:00}